Nirdizati: A Web-based Tool for Predictive Process Monitoring

### 2017-06-16 BPM17-demo-paper/paper.tex
abstract

\begin{abstract}
In this paper, we present a prototype of a predictive process monitoring engine for process workers and operational managers.
The developed solution, named \emph{Nirdizati}, is a configurable full-stack web application that supports users in selecting the preferred prediction method from the list of implemented methods and enables the continuous prediction of various performance indicators at runtime.
The results of the predictions, as well as the real-time summary statistics about the process execution, are presented in a dashboard that offers multiple visualization options.
The target audience of this demonstration includes process mining researchers as well as practitioners interested in exploring the potential of process monitoring.
\keywords{Process Mining, Predictive Process Monitoring, Machine Learning}
\end{abstract}

\section{Introduction} \label{sec:intro}
\emph{Predictive Monitoring}~\cite{PredictiveMonitoring} is an emerging paradigm based on the continuous generation of predictions and recommendations on what activities to perform and what input data values to provide, so that the likelihood of violation of business constraints is minimized. % and violations can be avoided.
In this paradigm, a user specifies a type of prediction or a measure of interest she is interested in. Based on an analysis of execution traces, the idea of predictive monitoring is to continuously provide the user with predictions and estimated values of the measure of interest. Such predictions generally depend both on: (i) the sequence of activities executed in a given case; and (ii) the values of data attributes after each activity execution in a case.

>>>>

\begin{abstract}
%In this paper, we present a prototype of a predictive process monitoring engine for process workers and operational managers.
%The developed solution, named \emph{Nirdizati}, is a configurable full-stack web application that supports users in selecting the preferred prediction method from the list of implemented methods and enables the continuous prediction of various performance indicators at runtime.
%The results of the predictions, as well as the real-time summary statistics about the process execution, are presented in a dashboard that offers multiple visualization options.
%The target audience of this demonstration includes process mining researchers as well as practitioners interested in exploring the potential of process monitoring.
In this paper, we present a prototype of a web-based application for predictive process monitoring that can be used by process workers and operational managers to predict the future development of a currently running process execution.
The implemented solution, named \emph{Nirdizati}, is a configurable full-stack web application that supports users in selecting the preferred prediction methods from a list of implemented algorithms and enables the continuous prediction of various measures of interest at runtime. The results of the predictions, as well as the real-time summary statistics about the process executions, are presented in a dashboard that offers multiple visualization options. The target audience of this demonstration includes process mining researchers as well as practitioners interested in exploring the potential of predictive process monitoring.
\keywords{Process Mining, Predictive Process Monitoring, Machine Learning}
\end{abstract}

\section{Introduction} \label{sec:intro}
\emph{Predictive Process Monitoring}~\cite{PredictiveMonitoring} is an emerging paradigm based on the continuous generation of predictions about the future values of user-specified measures of interest about a currently running process execution.
%and recommendations on what activities to perform and what input data values to provide, so that the likelihood of violation of business constraints is minimized. % and violations can be avoided.
In this paradigm, a user define the type of predictions she is interested in and a set of historical execution traces. Based on the analysis of these traces, the idea of predictive monitoring is to continuously provide the user with predictions and estimated values of the measure of interest. Such predictions generally depend both on: (i) the sequence of activities executed in a given case; and (ii) the values of data attributes after each activity execution in a case.
